Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-30 paper/paper.qmd
Updated figures

```{r pairplot}
#| warning: false
#| message: false
#| echo: false
numeric_data <- data %>% 
  select(where(is.numeric)) %>% 
  select(numeric_grade, pollscore, transparency_score) %>% 
  filter(complete.cases(.))

@@

>>>>

```{r pairplot}
#| warning: false
#| message: false
#| echo: false
#| label: fig-multicol
numeric_data <- data %>% 
  select(where(is.numeric)) %>% 
  select(numeric_grade, pollscore, transparency_score) %>% 
  filter(complete.cases(.))

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-pct
data %>% filter(candidate_name %in% c("Kamala Harris", "Donald Trump")) %>% 
  mutate(end_date = as.Date(end_date, format = "%m/%d/%y")) %>% 
  filter(end_date > as.Date("2024-01-01")) %>% 
  ggplot(aes(x = end_date, y = pct, color = candidate_name, group = candidate_name)) +
  geom_point(alpha = 0.2) +
  geom_smooth() +
  labs(
    title = "Polling Percentage over Time by Candidate",
    x = "End Date",
    y = "Polling Percentage (%)",
    color = "Candidate"
  ) +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_minimal() +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
